Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.

### 2019-03-20 msbframework/msbintro/msbintro.tex
Added notes for assisting with swedish translation. Added that the presentation is based upon the materials provided by MSB.

\title[Intro infosäk]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.
}
\author{Lennart Franked\footnote{Based on material written by
    Carina Bengtsson and Daniel Bosk}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.

  %Avdelningen för informations- och kommunikationssytem (IKS),\\
  %Mittuniversitetet, Sundsvall.
}

@@

\subsection{Identify and Analyse}
\begin{frame}{Overview}{\insertsubsectionhead}
  \begin{itemize}
    \item Analyse the external contexts~\footnote{Omvärldsanalys} and the organisation.
    \item Requires knowledge about how the current situation looks
      like~\footnote{Nulägesanalys}.
      \begin{itemize}
        \item Look over existing documentation.
        \item Discuss within the organisation.
      \end{itemize}
    \item Mapping of the informational assets\footnote{informationskartläggning}.
    \item Analyse the risks connected to the informational assets.
    \item Find suitable security measurements.
    \item Existing security measurements are controlled using a GAP-analysis
  \end{itemize}
\end{frame}

@@

\subsubsection{Organisational Analysis\footnote{Verksamhetsanalys}}
\begin{frame}{\insertsubsubsectionhead}
  \begin{itemize}
    \item Mapping
    \begin{itemize}
      \item Internal parties needs, requirements and expectations.
      \begin{itemize}
        \item Decision makers
        \item Object owners
        \item Co-workers
        \item Support units
      \end{itemize}
      \item Internal Prerequisites.
      \begin{itemize}
        \item Goals
        \item Strategies
        \item Organisational Culture
        \item Infrastructure
      \end{itemize}
      \item The organisations essential informational assets.
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\title[Intro infosäk]{%
  Introduction to\\
  Swedish Civil Contingencies Agency (MSB) methodological support for introducing \ac{isms}.
}
\author{Lennart Franked\footnote{Lecture is based upon the materials provided by
  MSB~\cite{msb_metodstod} and previous lectures written by Carina Bengtsson and
  Daniel Bosk}}
\institute[MIUN IST]{%
  Department of Informationsystem and Technologies (IST),\\
  Mid Sweden University, Sundsvall.
}

@@

\subsection{Identify and Analyse}
\begin{frame}{Overview}{\insertsubsectionhead}
  \begin{itemize}
    \item Analyse the external contexts~\note{Omvärldsanalys} and the organisation.
    \item Requires knowledge about how the current situation looks
      like~\note{Nulägesanalys}.
      \begin{itemize}
        \item Look over existing documentation.
        \item Discuss within the organisation.
      \end{itemize}
    \item Mapping of the informational assets\note{informationskartläggning}.
    \item Analyse the risks connected to the informational assets.
    \item Find suitable security measurements.
    \item Existing security measurements are controlled using a GAP-analysis
  \end{itemize}
\end{frame}

@@

\subsubsection{Organisational Analysis}
\begin{frame}{\insertsubsubsectionhead}
  \note{Verksamhetsanalys}
  \begin{itemize}
    \item Mapping
    \begin{itemize}
      \item Internal parties needs, requirements and expectations.
      \begin{itemize}
        \item Decision makers
        \item Object owners
        \item Co-workers
        \item Support units
      \end{itemize}
      \item Internal Prerequisites.
      \begin{itemize}
        \item Goals
        \item Strategies
        \item Organisational Culture
        \item Infrastructure
      \end{itemize}
      \item The organisations essential informational assets.
    \end{itemize}
  \end{itemize}
\end{frame}
